Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-01 sections/eval.tex
Update on Overleaf.

As depicted in Figure~\ref{fig:spgemm}, Finch achieves comparable performance with TACO on smaller matrices when we use the same datastructures, and significant improvements when we use better datastructures. For large sparse matrices, Finch outperforms TACO with an average speedup of 1.05.

@@

To evaluate the capabilities of Finch in graph applications, we assessed its performance in two fundamental graph algorithms: Breadth-First Search (BFS) and Bellman-Ford single-source shortest path. The graphs used were obtained from GraphBLAS~\cite{mattson2019lagraph}, including road networks (SNAP/roadNet-CA and GAP/GAP-road), characterized by bounded node degrees and long diameters, and scale-free graphs, where node degree distribution follows a power-law distribution and diameters are short. Direction-optimization~\cite{beamer2012direction} is crucial for achieving high performance in such scenarios.

>>>>

As depicted in Figure~\ref{fig:spgemm}, Finch achieves comparable performance with TACO on smaller matrices when we use the same datastructures, and significant improvements when we use better datastructures. For large sparse matrices, Finch outperforms TACO with an average speedup of 1.05 \changwan{(self)may remove this number for consistency with other exps. finch\_outer\_bytemap not explained.}.

@@

To evaluate the capabilities of Finch in graph applications, we assessed its performance in two fundamental graph algorithms: Breadth-First Search (BFS) and Bellman-Ford single-source shortest path. The graphs used were obtained from GraphBLAS~\cite{mattson2019lagraph}, including road networks (SNAP/roadNet-CA and GAP/GAP-road), characterized by bounded node degrees and long diameters, and scale-free graphs, where node degree distribution follows a power-law distribution and diameters are short. Direction-optimization~\cite{beamer2012direction} is crucial for achieving high BFS performance in such scenarios.
